Forecasting the 2024 US Presidential Election

### 2024-11-04 paper/paper.qmd
ujpdate appendix 2

@@

\begingroup
\small

**Introduction**: Thank you for participating in our survey to forecast the 2024 U.S. Presidential election outcome. Your responses will remain confidential, and participation is voluntary.

**Section 1: Eligibility Screening**:
  - U.S. citizenship and voter eligibility questions.

**Section 2: Demographics**:
  - Questions on age, gender, race, education, income, and region.

**Section 3: Political Views and Voting Intentions**:
  - Likelihood of voting, party affiliation, candidate choice, and issue importance.

**Section 4: Engagement and Information Sources**:
  - Questions about primary news sources and engagement with election coverage.

**End Message**: Thank you for your time. For survey inquiries, please contact [duanyi.su@mail.utoronto.ca](mailto:duanyi.su@mail.utoronto.ca).

@@

\newpage
# Additional data details

>>>>

```{r}
#| label: fig-all-obs
#| tbl-cap: Support Rates of Donald Trump and Kamala Harris by State
#| echo: false
#| warning: false
#| message: false
state_support_rates <- president_polls_cleaned_data %>%
  group_by(state, candidate_name) %>%
  summarise(avg_pct = mean(pct, na.rm = TRUE)) %>%
  ungroup()

# Correlation analysis
ggplot(state_support_rates, aes(x = state, y = avg_pct, fill = candidate_name)) +
  geom_bar(stat = "identity", position = "dodge", width = ) +
  labs(title = "Support Rates of Donald Trump and Kamala Harris by State",
       y = "Average Support Rate (%)",
       x = "State") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(president_polls_cleaned_data, aes(x = end_date, y = pct, color = candidate_name)) +
  geom_point(size = 0.5) +
  facet_wrap(~ state, scales = "free_y") +
  labs(title = "Support Rates of Donald Trump and Kamala Harris by State",
       y = "Support Rate (%)",
       x = "Date",
       color = "Candidate") +
  theme_minimal() +
  theme(legend.position = "bottom")
```

@@

**Title:**

  2024 U.S. Presidential Election Forecast Survey

**Introduction:**

  We appreciate your participation in this survey, which aims to forecast the outcome of the 2024 U.S. Presidential election. Your responses are essential for our research.

**Please note:**

  - Your answers will be treated with complete confidentiality.

- Participation in this survey is voluntary.

- We encourage you to provide honest and thoughtful responses.

- The survey is estimated to take about 5 minutes to complete.

- If you have any questions or concerns, feel free to reach out to our research team at [duanyi.su@mail.utoronto.ca](duanyi.su@mail.utoronto.ca) (Xinqi Yue, Yawen Tan, Duanyi Su).

Thank you for your valuable contribution! As a token of our appreciation, each participant will receive $5 upon completion of the survey.

**Section 1: About Eligibility**

  Are you a U.S. citizen?

  - Yes

- No (Please end Survey)

Do you meet your state’s residency requirements?

  - Yes

- No (Please end Survey)

Will you be 18 years old  or elder by the Election Day?

  - Yes

- No (Please end Survey)

Are you registered to vote by the voter registration deadline. (North Dakota does not require voter registration.)

- Yes

- No

- Wish to register later

**Section 2: About Demographics**

The following questions will help us understand the background characteristics of our respondents.

Which age group do you belong to?

- 18-29

- 30-44

- 45-64

- 65 or older

What is your gender?
- Male

- Female

- Prefer not to say

- Other

What is your race or ethnicity? Please select all that apply.
- White

- Black or African American

- Hispanic or Latino

- Asian

- Native American or Alaska Native

- Native Hawaiian or Other Pacific Islander

- Prefer not to say

- Other

Which U.S. state do you currently live in?

[answer box]

What region do you live in within your state?

- Rural

- Suburban

- Urban

- Prefer not to say

What is your political affiliation?

- Democratic

- Republican

- Independent

- Libertarian

- Green Party

- Prefer not to say

- Other

**Section 3: Voting Behavior and Intentions**

These questions focus on voting registration and plans for the upcoming election.

How likely is it that you will vote in the 2024 U.S. Presidential Election?

- Very likely

- Somewhat likely

- Somewhat unlikely

- Very unlikely

If the election were held today, which candidate would you most likely vote for?

- Donald Trump

- Kamala Harris

- Not sure

- Prefer not to say

- Other

How confident are you that your choice would remain the same by Election Day?

- Not at all confident

- Slightly confident

- Moderately confident

- Very confident

- Completely confident

**Section 4: Engagement with the Election**

This section aims to understand how actively our respondents follow and discuss the election.

How closely do you follow news and updates related to the 2024 U.S. Presidential Election?

- Very closely

- Somewhat closely

- Not very closely

- Not at all

How often do you discuss the 2024 U.S. Presidential Election with friends, family, or colleagues?

- Daily

- Weekly

- Occasionally

- Rarely

- Never

**Section 5: Additional Insights**

We appreciate any additional thoughts our respondents may have on the upcoming election.

Do you have any further comments or insights about the factors that might affect the 2024 U.S. Presidential Election? (optional)

[Answer box]

**End Message:**

Thank You for Completing the Survey!

We appreciate your time and thoughtful responses. Your participation is invaluable in helping us gather insights for our research on the 2024 U.S. Presidential Election forecast. Your answers will contribute to a more comprehensive understanding of voter trends and factors influencing this election.

If you have any further questions or would like to know more about this study, please feel free to reach out to our research team at [anjojoo.xu@mail.utoronto.ca](anjojoo.xu@mail.utoronto.ca).

As a thank you, each participant will receive a $5 reward shortly after survey completion.

@@

# Additional data details
